%% acknowledgments.tex

% From mitthesis package
% Version: 1.02, 2024/06/19
% Documentation: https://ctan.org/pkg/mitthesis

\chapter*{Acknowledgments}
\pdfbookmark[0]{Acknowledgments}{acknowledgments}


I would like to begin by expressing my gratitude to my advisor Prof Dr Arpan Banerjee for his invaluable guidance and support. Discussing my ideas with him and receiving critical feedback was an invaluable tool 
in troubleshooting the countless challenges I have faced during this project. Thank you for you patience and support throughout this journey.

I would also like to thank Shashwati Tripathi, a collaborator and support system. Her invaluable insights, unwavering faith in my hyperactivity, and tolerance of 
my ability to incessantly talk about my ideas were crucial to the success of this project.

I am grateful to my colleagues, Dhrubajoti, Vinitha, Azman, and Tanmay for their valuable inputs and continued support. I am grateful to all members of the lab for 
ensuring that I was never alone in my journey at the lab.

My heartfelt gratitude to my friends Vibha, Atharva and Lisha for continuous encouragement and support. Through countless midnight discussions, obscenely bad jokes, 
and the occasional existential crisis they have helped add colour to an otherwise monochrome journey.

Finally, I would to thank my mother and sister, their struggles and sacrifices have been the foundation of my journey. Without their support, I would not be where I 
am today. Their faith in my ambitions and dreams has been the fire that has kept me going through even the most unkind times. I am forever grateful for their presence 
in my life. 

